Exp1 - Opt w_max and {A,phi)

### 2018-03-15 voltagebudget/analysis/freq_analysis.Rmd
Added exp79 (slow frew) to figures

```{r, message=FALSE}
exp <- "77"
freqs <- c(8, 12, 20, 24, 30)

results <- NULL
for(freq in freqs){
  name <- paste("../data/exp", exp, "_d-2e-3_f", as.character(freq), ".csv", sep="")
  df <- read_csv(paste(name, sep=","))
  df %>%
    filter(n_spikes > 0) -> df

@@

# Process
results %>% 
  # Add delta_spikes
  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
  # Re-norm V_osc
  mutate(V_osc = V_osc - V_osc_ref) -> results

@@

```{r, fig.width=1.2, fig.height=0.8}
avg_results %>% 
  ggplot(aes(x=V_osc*1e3, y=variances, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  labs(x="V_osc (mvolt)", y="Variance (ms)") +
  scale_color_gradient(low="gold", high="darkgreen") +
  theme_classic() +
  theme(legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8))
```

>>>>

```{r, message=FALSE}
results <- NULL

# --------------------------
exp <- "77"
freqs <- c(24, 30)

for(freq in freqs){
  name <- paste("../data/exp", exp, "_d-2e-3_f", as.character(freq), ".csv", sep="")
  df <- read_csv(paste(name, sep=","))
  df %>%
    filter(n_spikes > 0) -> df

@@

# --------------------------
exp <- "79"
freqs <- c(6, 8, 10, 12, 14, 16, 18, 20)

for(freq in freqs){
  name <- paste("../data/exp", exp, "_d-2e-3_f", as.character(freq), ".csv", sep="")
  df <- read_csv(paste(name, sep=","))
  df %>%
    filter(n_spikes > 0) -> df

# --------------------------
# Process
results %>% 
  # Add delta_spikes
  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
  # Re-norm V_osc
  mutate(V_osc = V_osc - V_osc_ref) -> results

@@

```{r, fig.width=1.3, fig.height=0.8}
avg_results %>% 
  ggplot(aes(x=V_osc*1e3, y=variances, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  labs(x="V_osc (mvolt)", y="Variance (ms)") +
  scale_color_gradient(low="gold", high="darkgreen") +
  theme_classic() +
  theme(legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8))
```

### 2018-03-15 voltagebudget/analysis/paper_figures.Rmd
Added exp79 (slow frew) to figures

# --------------------------------------------------------------------
# Sweep A
exp <- "77"
freqs <- c(8, 12, 20, 30)

# Load
fig1 <- NULL
for(freq in freqs){
  name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
  df <- read_csv(paste(name, sep=","))
  df %>%
    filter(n_spikes > 0) -> df

@@

```{r, fig.width=2, fig.height=1.7}
fig2 %>% 
  ggplot(aes(x=V_osc*1e3, y=delta_spikes, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  labs(x=expression(V[o] (mvolt)), y="Spike count") +
  scale_color_gradient(low="gold", high="darkgreen") +
  scale_x_continuous(breaks=c(0, 4.0, 8.0, 12.0)) +
  theme_classic() +
  theme(legend.position="right", 
    legend.key.size = unit(.3, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p1

fig2 %>% 
  ggplot(aes(x=V_osc*1e3, y=errors*1e3, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  labs(x=expression(V[o] (mvolt)), y="Error (ms)") +
  scale_color_gradient(low="gold", high="darkgreen") +
  theme_classic() +
  scale_x_continuous(breaks=c(0, 4.0, 8.0, 12.0)) +
  theme(legend.position="none", 
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p2

fig2 %>% 
  ggplot(aes(x=V_osc*1e3, y=variances*1e3, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  labs(x=expression(V[o] (mvolt)), y="Variance (ms)") +
  scale_color_gradient(low="gold", high="darkgreen") +
  scale_x_continuous(breaks=c(0, 4.0, 8.0, 12.0)) +
  theme_classic() +
  theme(legend.position="none", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p3

@@

# Homeostatis - bigger budgets for more granular control.

>>>>

# --------------------------------------------------------------------
fig1 <- NULL

# --------------------------
exp <- "77"
freqs <- c(24, 30)

for(freq in freqs){
  name <- paste("../data/exp", exp, "_d-2e-3_f", as.character(freq), ".csv", sep="")
  df <- read_csv(paste(name, sep=","))
  df %>%
    filter(n_spikes > 0) -> df

# --------------------------
exp <- "79"
freqs <- c(6, 8, 10, 12, 14, 16, 18, 20)

for(freq in freqs){
  name <- paste("../data/exp", exp, "_d-2e-3_f", as.character(freq), ".csv", sep="")
  df <- read_csv(paste(name, sep=","))
  df %>%
    filter(n_spikes > 0) -> df

@@

```{r, fig.width=1.8, fig.height=1.5}
fig2 %>% 
  filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(x=V_osc/V_comp, y=delta_spikes, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  labs(x=expression(V[o]/V[c]), y="Spike count") +
  scale_color_gradient(low="gold", high="darkgreen") +
  # scale_x_continuous(breaks=c(0, 4.0, 8.0, 12.0)) +
  theme_classic() +
  theme(legend.position="right", 
    legend.key.size = unit(.3, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p1

fig2 %>% 
  filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  labs(x=expression(V[o]/V[c]), y="Error (ms)") +
  scale_color_gradient(low="gold", high="darkgreen") +
  theme_classic() +
  # scale_x_continuous(breaks=c(0, 4.0, 8.0, 12.0)) +
  theme(legend.position="none", 
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p3

fig2 %>% 
  filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(x=V_osc/V_comp, y=variances*1e3, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  labs(x=expression(V[o]/V[c]), y="Variance (ms)") +
  scale_color_gradient(low="gold", high="darkgreen") +
  # scale_x_continuous(breaks=c(0, 4.0, 8.0, 12.0)) +
  theme_classic() +
  theme(legend.position="none", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p2

@@
